### 2017-01-15 conclusion.tex
Bibliography issues corrected

In Chapter \ref{sec:paper1}, the occurence of radar backscatter durring nighttime in the polar cap was found to be much higher than expected, particularly given that raytracing simulations predict that the orthagonality condition is rarely met and therefore there should be little to no backscatter.  The proposed hypothesis to explain this discreperency is that polar patches, which are not typically well represented by ionospheric density models, occur frequently in the nighttime F region and, on average, enhance the background plasma density enough that propagation conditions are sufficient for HF radar backscatter to regularly be observed.  Experimental surveys of polar patches have shown low occurrence at nighttimes, however the occurrence of patches and their intensity increase at equinox, which is where frequent nighttime backscatter is predominantly observed.  The expected signature in the radar data from this kind of senario would be a night with a series of isolate ``patches'' of backscatter.  An example of such an event was presented, Figure \ref{whatever the hell THIS'll be}, but it is unknown how often events like this occur.  Additionally, the intensity and size of a patch nessesary to cause the radar beam to refract sufficiently must be established, possibly through further use of raytracing simulations with customizable density profiles.

One of the major drawbacks to linear GDI theory is its limitation of applicability only to long wavelengths, which means if the F region, it cannot be directly applicable to decameter-scale irregularities measured by HF radars.  Generally, it is assumed that some form of turbulent cascade connects plasma structures of different scale sizes in the ionosphere such that predictions made at large scales can still be applied to decameter-scale observations.  This helps explain some of the observations of asymmetry around polar patches.  This asymmetry was also confirmed in the GDI growth rate from the results shown in Chapter \ref{sec:paper2}.  However, these results also predicted anisotropy in the growth rate, which is more challenging to confirm from small-scale irregularity obsersavtions, although some evidence of such has been provided in Chapter \ref{sec:paper3}.  It may be possible to further the theoretical understanding of GDI at small scales by developing a three dimentional picture of it using kinetic theory.  \citet{Basu1995} developed such a formulation for a specific geometry throughout all altitudes within the ionosphere, but expanding this to general vector directions would most likely be extremely mathematically intensive.

@@

>>>>

In Chapter \ref{sec:paper1}, the occurence of radar backscatter durring nighttime in the polar cap was found to be much higher than expected \citep{Bristow2011}, particularly given that raytracing simulations predict that the orthagonality condition is rarely met and therefore there should be little to no backscatter.  The proposed hypothesis to explain this discreperency is that polar patches, which are not typically well represented by ionospheric density models, occur frequently in the nighttime F region and, on average, enhance the background plasma density enough that propagation conditions are sufficient for HF radar backscatter to regularly be observed.  Experimental surveys of polar patches have shown low occurrence at nighttimes, however the occurrence of patches and their intensity increase at equinox, which is where frequent nighttime backscatter is predominantly observed \citep{Rodger1996}.  The expected signature in the radar data from this kind of senario would be a night with a series of isolate ``patches'' of backscatter.  An example of such an event was presented, Figure \ref{whatever the hell THIS'll be}, but it is unknown how often events like this occur.  Additionally, the intensity and size of a patch nessesary to cause the radar beam to refract sufficiently must be established, possibly through further use of raytracing simulations with customizable density profiles.

One of the major drawbacks to linear GDI theory is its limitation of applicability only to long wavelengths, which means if the F region, it cannot be directly applicable to decameter-scale irregularities measured by HF radars.  Generally, it is assumed that some form of turbulent cascade connects plasma structures of different scale sizes in the ionosphere such that predictions made at large scales can still be applied to decameter-scale observations \citep{Tsunoda1988}.  This helps explain some of the observations of asymmetry around polar patches.  This asymmetry was also confirmed in the GDI growth rate from the results shown in Chapter \ref{sec:paper2}.  However, these results also predicted anisotropy in the growth rate, which is more challenging to confirm from small-scale irregularity obsersavtions, although some evidence of such has been provided in Chapter \ref{sec:paper3}.  It may be possible to further the theoretical understanding of GDI at small scales by developing a three dimentional picture of it using kinetic theory.  \citet{Basu1995} developed such a formulation for a specific geometry throughout all altitudes within the ionosphere, but expanding this to general vector directions would most likely be extremely mathematically intensive.

@@

\bibliographystyle{uafthesis}
\bibliography{references}
